\begin{process}
    The system design interview is an open-ended conversation. You are expected to lead it.
    \begin{enumerate}
        \item \textbf{Outline use cases, constraints, and assumptions}
        \begin{itemize}
            \item Gather requirements and scope the problem. Ask questions to clarify use cases and constraints. Discuss assumptions.
            \begin{itemize}
                \item Who is going to use it?
                \item How are they going to use it?
                \item How many users are there?
                \item What does the system do?
                \item What are the inputs and outputs of the system?
                \item How much data do we expect to handle?
                \item How many requests per second do we expect?
                \item What is the expected read to write ratio?
            \end{itemize}
        \end{itemize}
        
        \item \textbf{Create a high level design}
        \begin{itemize}
            \item Outline a high level design with all important components.
            \item Sketch the main components and connections.
            \item Justify your ideas.
        \end{itemize}

        \item \textbf{Design core components}
        \begin{itemize}
            \item Dive into details for each core component. 
            \item For example, if you were asked to design a URL shortening service, discuss:
            \begin{itemize}
                \item Generating and storing a hash of the full URL
                \begin{itemize}
                    \item MD5 and Base62
                    \item Hash collisions
                    \item SQL or NoSQL
                    \item Database schema
                \end{itemize}
                \item Translating a hashed URL to the full URL
                \begin{itemize}
                    \item Database lookup
                \end{itemize}
                \item API and object-oriented design
            \end{itemize}
        \end{itemize}
        
        \item \textbf{Scale the design}
        \begin{itemize}
            \item Identify and address bottlenecks, given the constraints. 
            \item For example, do you need the following to address scalability issues?
            \begin{itemize}
                \item Load balancer
                \item Horizontal scaling
                \item Caching
                \item Database sharding
            \end{itemize}
            \item Discuss potential solutions and trade-offs. Everything is a trade-off. Address bottlenecks using principles of scalable system design.
        \end{itemize}
        \item \textbf{Back-of-the-envelope calculations}
        \begin{itemize}
            \item 
        \end{itemize}
    \end{enumerate}
\end{process}

\subsection{Back-of-the-envelope calculations}
\subsubsection{Powers of 2 Table}
\begin{summary}
    \begin{center}
        \begin{tabular}{r l l l}
        \toprule
        \textbf{Power} & \textbf{Exact Value} & \textbf{Approx Value} & \textbf{Bytes} \\
        \midrule
        7  & 128 & & \\
        8  & 256 & & \\
        10 & 1,024 & 1 thousand & 1 KB \\
        16 & 65,536 & & 64 KB \\
        20 & 1,048,576 & 1 million & 1 MB \\
        30 & 1,073,741,824 & 1 billion & 1 GB \\
        32 & 4,294,967,296 & & 4 GB \\
        40 & 1,099,511,627,776 & 1 trillion & 1 TB \\
        \bottomrule
        \end{tabular}
    \end{center}
\end{summary}

\subsubsection{Latency numbers every programmer should know}
\begin{summary}
    \begin{center}
        \textbf{Latency Comparison Numbers}
        \begin{tabular}{l r r r l}
        \toprule
        \textbf{Operation} & \textbf{Time (ns)} & \textbf{Time (us)} & \textbf{Time (ms)} & \textbf{Notes} \\
        \midrule
        L1 cache reference & 0.5 & & & \\
        Branch mispredict & 5 & & & \\
        L2 cache reference & 7 & & & 14x L1 cache \\
        Mutex lock/unlock & 25 & & & \\
        Main memory reference & 100 & & & 20x L2 cache, 200x L1 cache \\
        Compress 1 KB with Zippy & 10,000 & 10 & & \\
        Send 1 KB over 1 Gbps network & 10,000 & 10 & & \\
        Read 4 KB randomly from SSD* & 150,000 & 150 & & \textasciitilde1 GB/sec SSD \\
        Read 1 MB sequentially from memory & 250,000 & 250 & & \\
        Round trip within same datacenter & 500,000 & 500 & & \\
        Read 1 MB sequentially from SSD* & 1,000,000 & 1,000 & 1 & \textasciitilde1 GB/sec SSD, 4x memory \\
        HDD seek & 10,000,000 & 10,000 & 10 & 20x datacenter roundtrip \\
        Read 1 MB sequentially from 1 Gbps & 10,000,000 & 10,000 & 10 & 40x memory, 10x SSD \\
        Read 1 MB sequentially from HDD & 30,000,000 & 30,000 & 30 & 120x memory, 30x SSD \\
        Send packet CA $\rightarrow$ NL $\rightarrow$ CA & 150,000,000 & 150,000 & 150 & \\
        \bottomrule
        \end{tabular}
    \end{center}
    \vspace{1em}

    \begin{itemize}
        \item 1 ns = $10^{-9}$ seconds
        \item 1 $\mu$s = $10^{-6}$ seconds = 1,000 ns
        \item 1 ms = $10^{-3}$ seconds = 1,000 $\mu$s = 1,000,000 ns
    \end{itemize}
    \vspace{1em}

    \begin{itemize}
        \item Read sequentially from HDD at 30 MB/s
        \item Read sequentially from 1 Gbps Ethernet at 100 MB/s
        \item Read sequentially from SSD at 1 GB/s
        \item Read sequentially from main memory at 4 GB/s
        \item 6--7 world-wide round trips per second
        \item 2,000 round trips per second within a data center
    \end{itemize}
\end{summary}
